MATH 3610 - Project \#1

### 2015-09-27 proj1.tex
Adding a log: work associated with parts of the tex file. Deterministic model for disease spread with vaccins

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\rfoot{\thepage}
\lfoot{\includegraphics[height=20pt]{Logo}}

@@

\begin{tikzpicture}[scale=2.0]
	\coordinate[label=below:{$0$}] (origin) at (0,0);
	\draw[<->, thick] (0,2) node (saxis) [above] {$S$}
	|- (3,0) node (taxis) [right] {$t$};

	\coordinate[label=left:{$K$}] (sintercept) at (0,1.5);
	\coordinate[label=below:{$\frac{K}{r_v}$}] (tintercept) at (2.2,0);
	\draw (sintercept) -- (tintercept);
	\fill[gray!20, opacity=0.8] (origin) -- (sintercept) -- (tintercept) -- cycle;

	\draw[dotted] (sintercept) -- (3.0, 1.5);
	\node (valid) at (0.7,0.4) {Valid Region};
	\node (endregion) at (2.3, 1.0) {No-Change Region};
\end{tikzpicture}

@@

\paragraph{}
\pgfplotstableread[col sep = comma]{data/s.csv}\mydata
\begin{tikzpicture}
	\begin{axis}[
		legend pos = south east,
		xmin = 0,
		xmax = 6,
		ymin = 0,
		ymax = 1.3,
		ylabel = {$S(t)$ (units of total population)},
		xlabel = {$t$}
	]
	\foreach \index in {1, ..., 35} {%
		\addplot[mark=""] table[x index = {0}, y index = {\index}]{\mydata};
	}
	\addplot[mark=""] {1 - x * 0.2};
	\end{axis}
\end{tikzpicture}
\paragraph{}

>>>>

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\rfoot{\thepage}

@@

\includegraphics[width=0.5\textwidth]{figures/admissible-region.pdf}

@@

\includegraphics[width=0.5\textwidth]{figures/vaccination-model-curves-varying-s.pdf}

\subsection{Pareto Optimizing Between Two Independent Populations}

The model above modeled how one population responds to a combination
	of disease spreading and vaccines.
The model depends on $K$, the total population, $S(0)$, the initial
	number of sick people, $r$, the rate of infection growth, 
	and $r_v$, the vaccination rate.
Of these parameters, in a real world setting, we can expect to know $K$
	very precicely from census data, approximate $S(0)$ as small,
	have very little idea about $r$, and control $r_v$.

I want to extend this problem to two independant populations. 
Each population will get different sets of constants,
	$K_1$ and $K_2$, $S_1(0)$ and $S_2(0)$, $r_1$ and $r_2$.
The goal will be to figure out how to optimally allocate the
	vaccines between the two populations.
The decision variable, $d$, will be the fraction of the total vaccination
	rate I allocate to each population.
Population 1 will be vaccinated at a rate $d r_v$, while population
	2 will be vaccinated at a rate $(1 - d) r_v$.
In this model, I try to minimize the final number of sick people in
	each population.
This will give me a pareto front.

The following collection of pareto fronts comes from keeping the disease
	growth rate the same for both, and varying its magnitude.

\includegraphics[width=0.5\textwidth]{figures/vaccination-model-same-r-pareto-curves.pdf}

This collection of pareto fronts comes from keeping the growth
	rate for population 2 the same, and varying the growth
	rate of population 1.

\includegraphics[width=0.5\textwidth]{figures/vaccination-model-different-r-pareto-curves.pdf}
